Cohomology Theories, Triangulated Categories, and Applications\vspace{-1ex}

### 2019-05-22 Homological Algebra Notes/Hom Alg.tex
update

>>>>

\section{May 17, 2019}
Recall that today we will have extra class at 5pm today. Cody is going to give his talk!

\subsection{The Bar Resolution}
We begin with a non-standard presentation of the Bar resolution. Consider 
\[\cdots\to (\bbZ G)^2\to \bbZ G\to \bbZ\]
where the differential takes $(g_0,\dots,g_n)\in(\bbZ G)^{n+1}$ to $\sum_i(-1)^i(g_0,\cdots,\widehat{g_i},\cdots,g_n)$.
\begin{prop}
	This is a free resolution of $\bbZ$ as a $\bbZ G$ module.
\end{prop}
\begin{prf}
	It suffices to show that this is a resolution (i.e. that it is contractible). Thus we want to 
	construct the homotopy:
	\[s(g_0,\cdots,g_n)=(e,g_0,\cdots,g_n)\]
	which amounts to taking an $n$-simplex and embedding it into an $(n+1)$-simplex as a face.

	Then we can compute 
	\begin{align*}
		ds+sd(g_0,\cdots,g_n)&=d(e,g_1,\cdots,g_n)+s\left(\sum_i(-1)^i(g_0,\cdots,\widehat{g_i},\cdots,g_n)\right)\\
		&= (g_0,\cdots,g_n)-\sum_{i}(-1)^i(e,g_1,\cdots,\widehat{g_i},\cdots,g_n)+s\left(\sum_i(-1)^i(g_0,\cdots,\widehat{g_i},\cdots,g_n)\right)\\
		&= (g_0,\cdots,g_n)
	\end{align*}
	proving the statement.
\end{prf}
\begin{rmk}
	Notice that $(\bbZ G)^{n+1}$ is a free $\bbZ G$ module of rank $|G|^n$ with basis 
	\[[g_1|\cdots|g_n]=(e,g_1,g_1g_2,\dots,g_1\cdots g_n).\]
\end{rmk}
\begin{rmk}
	We can define the differential on the basis elements:
	\[d:=\sum_0^{n}(-1)^id_i:(\bbZ G)^{n+1}\to(\bbZ G)^n\]
	where $d_i:\bbZ G^{n+1}\to\bbZ G^n$ is given by
	\[d_i([g_1|\dots|g_n])=\left\{\begin{array}{lr}
		g_1[g_2|\dots|g_n],& i=0\\
		\left[g_1|\dots |g_ig_{i+1}|\dots|g_n \right], & i = n\\
		\left[g_1|\dots|g_{n-1}\right], & i = n.
	\end{array}\right.\]
\end{rmk}
\begin{defn}
	If we set $B_n=\bbZ G^{n+1}$, then $(B_\bullet, d)$ is called the \textbf{Bar resolution} of $\bbZ$.
\end{defn}
\begin{defn}
	If $D_\bullet$ is the subcomplex of $B_\bullet$ generated by all elements $[g_1|\dots|g_n]$ such that some $g_i=e$,
	then the quotient $B_\bullet/D_\bullet=\overline{B}_\bullet$ is called the \textbf{normalized Bar complex.}
\end{defn}
\begin{prob}
	Write down both the Bar and normalized Bar resolutions of $\bbZ$ using $G=\bbZ/2$ and compare.
\end{prob}

\subsection{Hochschild Complex for $H^\ast(G,M)$}
Begin with the Bar resolution $B_\bullet\to \bbZ$ and apply $\Hom_G(-,M)$, giving us a cochain complex. It will help to notice 
that $\Hom_G(B_n,M)\cong\Hom_{\bbZ G}(\bbZ G^{n+1},M)\cong\Hom_\bbZ(\bbZ G^n,M)$, which is equal to the set of 
(set!) functions $f:G^n\to M$ extended $\bbZ$-linearly. 
\begin{defn}
	$C^n(G,M)$ is the set of all linear combinations of set maps $f:G^n\to M$.
\end{defn}
\begin{rmk}
	Notice $C^n(G,M)\cong \Hom_G(\bbZ G^{n+1},M)$.
\end{rmk}
Then we can compute the induced differential $d_n:C^n(G,M)\to C^{n+1}(G,M)$ to be 
\begin{align*}
	(df)(g_1,\dots,g_{n+1})&- g_1f(g_2,\dots,g_{n+1})+\cdots+(-11)^if(g_1,\dots,g_ig_{i+1},\dots,g_{n+1})\\
	&\qquad\qquad+\cdots+(-1)^nf(g_1,\dots,g_n)
\end{align*}

\begin{cor}
	The Hochschild complex $C^\bullet$ computes $H^\ast(G,M).$
\end{cor}

\begin{defn}
	Let $R$ be a ring, $M$ an $(R,R)$-bimodule. Then a map of abelian groups $d:R\to M$ is called 
	a \textbf{derivation} if
	\[d(rs)=rd(s)+d(r)s.\]
\end{defn}
\begin{defn}
	If $M$ is a $\bbZ G$ (left) module and $d:\bbZ G\to M$ is such that 
	\[rd(s)+d(r)\]
	$d$ is called a \textbf{crossed homomorphism.}
\end{defn}
\begin{rmk}
	This essentially arises by considering a derivation on a module where the right action is defined to be trivial! This is sort of what is happening
	with the derivation in the Hochschild complex.
\end{rmk}
\begin{rmk}
	Notice that $d^1f(g_1,g_2)=g_1f(g_2)-f(g_1g_2)+f(g_1)$. If $d^1f=0$ then we call $f$ a cocycle (as per usual).
	So then the \textbf{cocycle condition on $C^1(G,M)$} is 
	\[f(g_1g_2)=g_1f(g_2)+f(g_1)\]
	or exactly the crossed homomorphisms/derivations.

	This gives us a nice characterization:
	\[H^1(G,M)\cong\{\text{crossed homomorphisms}\}/\{\text{principal crossed homomorphisms}\}.\]
\end{rmk}

\section{Talk: Lie Algebra Cohomology}
\subsection{Geometric Notions}
Let $G$ be a Lie group, a smooth manifold with smooth multiplication and inverse maps. Let $\frakg$ be $\operatorname{Lie}(\frakg)$
And consider the complex $\Omega^\bullet(G),$ the complex of $k$-forms on $G$ with differential given by the exterior derivative.

\begin{defn}
	$H^\ast_{dR}(G)$ is just the homology of $\Omega^\bullet(G)$.
\end{defn}

\begin{defn}
	Let $\Omega^\bullet_L(G)$ be the complex of left-invariant forms, $\{\omega\in\Omega^\ast(G)|L_g^\ast\omega=\omega\}$.
\end{defn}
\begin{rmk}
	A key fact to showing that this is indeed a complex is that the exterior derivative commutes with pullbacks.
\end{rmk}

\begin{thm}
	$\iota:\Omega_L^\bullet(G)\to\Omega^\bullet(G)$ is a quasi-isomorphism when $G$ is compact and connected.
\end{thm}
\begin{prf}
	(Sketch) For injectivity, suppose $\iota^\ast[\omega]=0\in H_{dR}^\ast(G)$. Then $\omega=d\mu$ for some $\mu$.
	Set $I(\omega)=\int_G L_g^\ast\omega dg$ (where this is called the Haar measure). But then after checking lots 
	of fiddly facts, you can show 
	\[\omega=I(\omega)=I(d\mu)=dI(\mu)\]

	For sujectivity, notice that the natural pairing $\langle[z],[w]\rangle=\int_z w$ where $[z]$ is a class in the homology  and $[w]$ is in the cohomology,
	then since any other representative for $[z]$ differs by a boundary the integral in unaffected and since any other representative in $[w]$ 
	differs by a coboundary (exact form), the integral is also unafected by this.

	Then there is some integration computations that go through lots of replacing things with other representatives (since $[z]=[L_g(z)]$ and $\iota^\ast[I(\omega)]=[\omega]$).
\end{prf}

For the next step we want to restrict to the identity. Notice that $\varepsilon:\Omega_L^\ast(G)\to(\wedge^\ast\frakg)^\ast$
is a well-defined map (here we send each form to its restriction to the identity: $\varepsilon(\omega)=\omega_e$).

Notice 
\begin{align*}
	\varepsilon(d\omega)(X_1|_e,\dots,X_n|_e)&=d\omega(X_1,\dots,X_n)(e)\\
	&=\sum_1^nX_i(\omega(X_1,\dots,\hat X_i,\dots,X_n))(e)+\sum_{i<j}([X_i,X_j],X_1,\dots,\hat X_i,\dots,\hat X_j,\dots,X_n)(e)
\end{align*}
and since the first term in the sum is zero (why?) the latter part is exactly the differential we want:
\[\delta\alpha(X_1,\dots,X_n)=\sum_{i<j}([X_i,X_j]_e,X_1|_e,\dots,\hat X_i|_e,\dots,\hat X_j|_e,\dots,X_n|_e)\]

\begin{thm}
	$H_L^\ast(G)\cong H^\ast(\frakg)$. Furthermore $H_{dR}^\ast(G)\cong H^\ast(\frakg)$.
\end{thm}
\begin{rmk}
	Note that $H^\ast(\frakg)$ is the cohomlogy of the $(\wedge^\ast\frakg)^\ast$
\end{rmk}
\subsection{Algebraic Notions}
Let $k$ be a commutative ring, $\frakg$ be a Lie algebra, and $\calU(\frakg)$ its universal enveloping algebra.

Notice that there is a functor from $k$ modules to $\frakg$ modules that gives any module $M$ a trivial $\frakg$ action. Recall the definition 
of invariants $(-)^\frakg$ ($M^\frakg=\{m\in M|xm=0\}$) and coinvariants $(-)_\frakg$ ($M_\frakg=M/\frakg M$).

The plan of attack is to show that these functors have adjoints and thus are exact on one side, and then we can talk about derived functors.

\begin{lem}
	$(-)^\frakg$ is right adjoint to the trivial $\frakg$-module functor. $(-)_\frakg$ is left adjoint to the same functor.
\end{lem}
\begin{cor}
	Thus $(-)^\frakg$ and $(-)_\frakg$ are left and right exact, respectively.
\end{cor}
\begin{lem}
	Let $\frakg$ be a Lie algebra. Then we have an equivalence of categories (isomorphism actually!)
	\[\frakg\text{-}\mathbf{mod}\cong \mathcal U\frakg\text{-}\mathbf{mod}\]
\end{lem}
\begin{rmk}
	Since $\mathcal U\frakg$-$\mathbf{mod}$ has enough projectives, so does $\frakg$-$\mathbf{mod}$.
\end{rmk}
\begin{defn}
	We write $H_\ast(\frakg,M)$ to be the left erived functor $L_\ast(-)_\frakg(M)$ and $H^\ast(\frakg,M)=R^\ast(-)^\frakg(M)$.
	These are the (co)homology groups of $\frakg$ with coefficients in $M$.
\end{defn}

How does this relate to $\Ext$ and $\Tor$?
\begin{rmk}
	If $M$ is a $\frakg$-module, then we can give $M$ a $\calU\frakg$ action in the following way:
	\[(x_1\otimes\cdots\otimes x_n)\cdot m=(x_1(x_2(\cdots(x_nm))))\]
\end{rmk}
\begin{thm}
	sIf $M$ is a $\frakg$-module, then 
	\[H_\ast(\frakg,M)=\Tor_\ast^{\calU\frakg}(k,M)\]
	and 
	\[H^\ast(\frakg,M)\cong\Ext_{\calU\frakg}^\ast(k,M).\]
\end{thm}

Here we need the PBW theorem, so we need to assume now that $\frakg$ is free as a $k$-module.
\begin{defn}
	Let $V_p(\frakg)=\calU\frakg\otimes_k\wedge^p\frakg$, where $V_0=\calU\frakg$ and $V_1=\calU\frakg\otimes\frakg$.

	Let $\varepsilon:\calU\frakg\to k$ be the augmentation map. Let $d:V_1(\frakg)\to V_0(\frakg)$
	to be the multiplication map $d(u\otimes x)=ux$ and more generally, 
	\[d(u\otimes x_1\wedge\cdots\wedge x_n)=\theta_1+\theta_2\]
	where
	\[\theta_1=\sum_1^n(-1)^{i+1}(ux_1\wedge\cdots\wedge\hat x_i\wedge\cdots\wedge x_n)\]
	and 
	\[\theta_2=\sum_{i<j}(-1)^{i+j}u\otimes[x_i,x_j]\wedge x_1\wedge\cdots\wedge\hat x_i\wedge\cdots\wedge \hat x_j\wedge\cdots\wedge x_n\]

	Then $V_\bullet(\frakg)$ with the above differential is called the \textbf{Chevalley-Eilenberg complex} for $\frakg$
\end{defn}

\begin{thm}
	$V_\bullet(\frakg)\to k$ is a projective resolution.
\end{thm}
\begin{rmk}
	This needs spectral sequences as well as the PBW theorem.
\end{rmk}
\begin{thm}
	If $M$ is a left $\frakg$-module, then the cohomology modules $H^\ast(\frakg,M)$ are the cohomology of the complex 
	\[\Hom_\frakg(V(\frakg),M)=\Hom_\frakg(\calU\frakg\otimes\wedge^\ast\frakg,M)\cong\Hom)k(\wedge^\ast\frakg,M)\]
\end{thm}

\section{May 20, 2019}
Recall that we hat just said that $H^1(G,M)$ was crossed homomorphisms module principal crossed homomorphisms.

Notice that when $M$ is trivial, a crossed homomorphism is precisely a group homomorphism and since the 
principle ones are zero, 
\[H^1(G,M)=\Hom_\Grp(G,M)=\Hom_\Ab(G/[G,G],M)\]
\begin{cor}
	If $G$ is perfect ($G=[G,G]$) then $H^1(G,\bbZ)=0$.
\end{cor}
\begin{rmk}
	In fact, $H_1(G,\bbZ)=G/[G,G]$.
\end{rmk}

\subsection{$H^2$}
Now let $A$ be an ableian group and $G$ module. Recall that 
\[0\to A\to E\to G\to 1\]
(a short exact sequence in $\Grp$) is called an extension of $G$ by $A$. Then we can show that (or let Weibel or Dummit \& Foote show us)
\[H^2(G,A)\cong \{0\to A\to E\to G\to 1\}/\sim\]
Check out Weibel 6.6.3.

\subsection{Triangulated Categories}
Recall the definition of triangulated categories from James' class or from my notes o
n Brown Representability:
\begin{defn}
	Let $\cal C$ be a $k$-linear additive category with a \textbf{suspension} or \textbf{shift} functor (auto-equivalence, actually)
	\[\Sigma:\cal C\to\cal C.\]

	Then $({\calC}, \Sigma ,D)$ is \textbf{triangulated} category where $D$ is a full, nonempty subcategory $D\subseteq\Delta(\cal C)$
	with shift functor $\Sigma$ of $D$ and we have the following axioms:
	\begin{itemize}
		\item (\textbf{TR0}) $0\to X\xrightarrow{\id} X\to 0$ is in $D$ for each $X\in \cal C$ and furthermore $D$ is closed under both shifts and triangle isomorphisms.
		\item (\textbf{TR1}) [\textit{Mapping Cone Axiom}] For any $f:X\to Y$ in $\cal C$, there is a triangle
		\[X\xrightarrow{f} Y\to Z\to\Sigma X\]
		\item (\textbf{TR2}) [\textit{Rotation Axiom}] If $F\in D$, then $\mathscr R(F),\mathscr R^{-1}(F)\in D$
		\item (\textbf{TR3}) [\textit{Morphism Axiom}] Given two triangles 
		\begin{center}
			\begin{tikzcd}
				X\ar[r]\ar[d,"f"] & Y\ar[r]\ar[d,"g"] & Z\ar[r]\ar[d,"h",dashed] & \Sigma X\ar[d,"\Sigma f"]\\
				X'\ar[r] & Y'\ar[r] & Z'\ar[r] & \Sigma X'
			\end{tikzcd}
		\end{center}
		with maps $f$ and $g$, there exists an $h:Z\to Z'$ such that the above diagram commutes.
		\item (\textbf{TR5}) [\textit{Octahedral Axiom}] Given three triangles: $X\xrightarrow{u}Y\to Z'\to\Sigma X$, $Y\xrightarrow{v}Z\to X'\to\Sigma Y$
		and $X\xrightarrow{v\circ u} Z\to Y'\to\Sigma X$. Then there is a triangle $Z'\to Y'\to X'\to\Sigma Z'$ such that
		\begin{center}
			\begin{tikzcd}
				X\ar[dr,"u"]\ar[rr,"v\circ u",bend left] && Z\ar[rr,bend left]\ar[dr] && X'\ar[rr,dashed,bend left]\ar[dr] && \Sigma Z'\\
				& Y\ar[ur,"v"]\ar[dr] && Y'\ar[ur,dashed]\ar[dr] && \Sigma Y\ar[ur] &\\
				&& Z'\ar[rr,bend right]\ar[ur,dashed] && \Sigma X\ar[ur] &&
			\end{tikzcd}
		\end{center}
	\end{itemize}
\end{defn}
\begin{rmk}
There are two other representations of the octahedral axiom that are sometimes more helpful:
\begin{center}
	\begin{tikzcd}
		X\ar[r,"u"]\ar[d,"\sim"] & Y\ar[r]\ar[d,"v"] & Z'\ar[r]\ar[d,dashed] &\Sigma X\ar[d,"\sim"]\\
		X\ar[r,"v\circ u"] & Z\ar[r]\ar[d] & Y'\ar[r]\ar[d,dashed] &\Sigma X\ar[d,"\Sigma u"]\\
		& X'\ar[r,"\sim"] \ar[d] & X'\ar[r]\ar[d,dashed] & \Sigma Y\\
		&\Sigma Y\ar[r] & \Sigma Z' &
	\end{tikzcd}
\end{center}

\begin{center}
	\begin{tikzcd}
		&& & X\ar[dl,"u"]\ar[dd,"v\circ u"] &\\
		&& Y\ar[dr,"v"]\ar[ddll] & &\\
		&& & Z\ar[d]\ar[dr] &\\
		Z'\ar[rrr,dashed] && & Y'\ar[r,dashed] & X'
	\end{tikzcd}
\end{center}

\begin{center}
	\begin{tikzcd}
		A\ar[rr,"f"]\ar[rrrr,bend left,"g\circ f"] & & B\ar[rr,"g"]\ar[dl] & & C\ar[ddll,bend left,dotted]\ar[dl]\\
		& C'\ar[ul,dotted]\ar[dr] & & A'\ar[ul,dotted]\ar[ll,dotted] &\\
		& & B'\ar[ur]\ar[uull,dotted, bend left] & &
	\end{tikzcd}
\end{center}
Above dotted lines refer to shifting.
\end{rmk}
\begin{lem}
	Say that $A\xrightarrow{u}B\xrightarrow{v}C\to\Sigma A$ is exact. Then $v\circ u=0$.
\end{lem}
\begin{prf}
	Just complete the morphism $(\id_A,u)$ to a triangle morphism. This gets it!
\end{prf}
\begin{ex}
	$\K(\Ch(\Rmod))$ is triangulated with triangles being all those in $\Delta(\calC)$ isomorphic to $A\xrightarrow{f}B\to \cone(f)\to \Sigma A$.
\end{ex}

\section{May 22, 2019}

### 2019-05-22 Triangulated Categories/Tri Cat.tex
update

% Document-Specific Macros
\newcommand*{\dgVectk}{\mathbf{dgVect}_k}
\newcommand*{\dgmodA}{\mathbf{dgmod}\text{-}A}
\newcommand*{\modA}{\mathbf{mod}\text{-}A}
\newcommand*{\Amod}{A\text{-}\mathbf{mod}}

@@

>>>>

% Document-Specific Macros
\newcommand*{\dgVectk}{\mathbf{dgVect}_k}
\newcommand*{\dgmodA}{\mathbf{dgmod}\text{-}A}
\newcommand*{\modA}{\mathbf{mod}\text{-}A}
\newcommand*{\Amod}{A\text{-}\mathbf{mod}}
\DeclareMathOperator{\depth}{depth}

@@

\section{May 17. 2019}
I missed a day but they talked about dualizing complexes some more and what they imply.

Let's do an example of the day:
\begin{ex}
	Let $A$ be a finite dimensional algebra over $k$. Then $R=A^\ast=\Hom_k(A,k)$ is finite dimensional over $k$. Then we claim that $R$
	is a dualizing complex over $(A,A)$. To see this, we must check:
	\begin{itemize}
		\item $H^i(R)=A^\ast$ for $i=0$ and is zero otherwise.
		\item $\injdim_AR=\injdim_AA^\ast=0$
		\item $R\Hom_A(R,R)=Hom_A(A^\ast,A^\ast)=\Hom_A(A,A)=A$.
	\end{itemize}
\end{ex}

\subsection{Proving the Dualizing Theorem}
\begin{defn}
	$R$ is a dualizing complex over $(A,B)$ if we have functors 
	\[\bbD=R\Hom_A(-,R):\Db_{fg}(\Amod)\to \Db_{fg}(\mathbf{mod}\text{-}B)\]
	and $\bbD^\circ=R\Hom_{B^{op}}(-,R)$ in the other direction.
\end{defn}
\begin{lem}
	Let $W$ be a complex of $(A,B)$ bimodules and let $X$ be a complex of $A$-modules and $Y$ a complex of $B^{op}$-modules. Then 
	\[\Hom_{\Ch(\Amod)}(X,\Hom_{\Ch(B\text{-}\mathbf{mod})}(Y,W)\cong\Hom_{\Ch(\mathbf{mod}\text{-}B)}(Y,\Hom_{\Ch(\Amod)}(X,W))\]
\end{lem}
\begin{thm}[Dualizing Theorem]\label{thm-dualizing}
	$(\bbD,\bbD^\circ)$ induces a contravariant equivalence between $\Db_{fg}(\Amod)$ and $\Db_{fg}(\mathbf{mod}\text{-}B)$
\end{thm}
\begin{rmk}
	We are looking to construct a natural isomorphism between the identity functor on $\Db_{fg}(\Amod)$ to $\bbD^\circ\bbD$.
\end{rmk}
\begin{lem}
	Let $W$ be a complex of $(A,B)$-bimodules and let $X$ and $Y$ be chains in $\Amod$ and $\mathbf{mod}\text{-}B$, respectively. Then 
	\[R\Hom_A(X,R\Hom_{B^{op}}(Y,W))\cong R\Hom_{B^{op}}(Y,R\Hom_A(X,W)).\]
\end{lem}
\begin{lem}
	Under the same conditions as above,
	\[\Hom_{\D(\Amod)}(X,R\Hom_{B^{op}}(Y,W))\cong\Hom_{\D(\mathbf{mod}\text{-}B)}(Y,R\Hom_A(X,W))\]
\end{lem}
\begin{cor}
	$R\Hom_{B^{op}}(-,W)$ and $R\Hom_A(-.W)$ is an adjoint pair. This gives us the map $\eta:1\to\bbD^\circ\bbD$.
\end{cor}
\begin{lem}
	Let $F$ and $G$ be two triangulated functors from $\calT_1\to\calT_2$ and $\eta:F\to G$ be a natural transformation. Then 
	if we let $S=\{X\in\calT|\eta_X:F(X)\to G(X)\text{ is an isomorphism}\}$, then $S$ is a triangulated subcategory.
\end{lem}
\begin{cor}
	It is a fact that the triangulated subcategory of $\D(\Amod)$ generated by $A$ is $\D_{perf}(\Amod)$. Thus, $\D_{perf}(]Amod)\subseteq S$.
	Thus in particular $\eta_X:X\mapsto\bbD^\circ\bbD(X)$ is an isomorphism for all $X\in\D_{perf}(\Amod)$.
\end{cor}
\begin{cor}
	$\bbD$ and $\bbD^\circ$ induce a contravariant equivalence between $\D_{perf}(\Amod)$ and $\D_{perf}(\mathbf{mod}\text{-}B).$
\end{cor}

\begin{defn}
	Let $X$ be a complex of $A$-modules. Then define $X_{[a,b]}$ to be 
	\[X^i_{[a,b]}=X^i\]
	whenever $i\in[a,b]$ and zero otherwise. Same for the differentials. This is a complex (obvious).
\end{defn}

\begin{lem}
\begin{itemize}
	\item If $X_{[b,\infty)}=0$, then there exists an ``embedding'' morphism $X_{[a,b]}\to X$.
	\item If $X_{(-\infty,a]}=0$ then there exists a ``projection'' morphism $X\to X_{[a,b]}$.
\end{itemize}
\end{lem}
\begin{lem}
	let $X$ be  a complex over $A$ such that $X=X_{[-b,b]}$. Let $Y$ and $Z$ be two complexes such that 
	\[Y_{[-c,c]}=Z_{[-c,c]}.\]
	Then 
	\[\Hom_{\Ch(\Amod)}(X,Y)_{[-(c-b),c-b]}=\Hom_{\Ch(\Amod)}(X,Z)_{[-(c-b),c-b]}\]

	This still holds if you switch the arguments in $\Hom$.
\end{lem}
\begin{cor}
	If $X$ and $Y$ ``agree locally'' as above, then $\bbD(Y)$ and $\bbD(Z)$ agree locally. This is slightly confusing since 
	we're working in the derived category here, but this means that they have isomorphic cohomology in some range.
\end{cor}

\begin{cor}
	$\bbD^\circ\bbD(Y)$ and $\bbD^\circ\bbD(Z)$ agree locally.
\end{cor}

\begin{prf}[of~\ref{thm-dualizing}]
	We need to show that $H^i(P)\cong H^i(\bbD^\circ\bbD(P))$ for all $i$. Fix $i$.

	Then call $Q=P_{[-c,c]}$ for $c>> i+2b$ and then $H^i(Q)\cong H^i(P)$ and looking at the naturality square everything is an isomoprhism and we're done.
\end{prf}

\section{May 20, 2019}
Today we will discuss homological identities.

\begin{defn}
	If $A$ is an algebra over $k$, it is called \textbf{local} if $A/J(A)\cong k$, where $J(A)$ is the Jacobson radical.
\end{defn}

\begin{thm}[Bass]
	Let $A$ be a local Noetherian algebra with balanced dualizing complex. Let $M$ be a finitely genreated left $A$-module with finite injective 
	dimensions. Then 
	\[\injdim M=\operatorname{depth}A<\infty.\]
\end{thm}
\begin{rmk}
	We haven't yet defined a balanced dualizing complex but we will. Later we will also see some theorems regarding 
	existence of such complexes.
\end{rmk}

\subsection{(Non)Example of the Day}
\begin{ex}
	There is an Artinian algebra $A$ such that for any algebra $B$, there is \textbf{no} dualizing complex over $(A,B)$. The construction 
	is quite complicated, but it works. Note that in particular $A$ cannot be finite dimensional since we saw that 
	the dual of $A$  is a dualizing complex for $A$ when it is.
\end{ex}
\begin{ex}
	There is an Artinian algebra $A$ such that
	\begin{itemize}
		\item There is no dualizing complex over $(A,A)$
		\item There is a dualizing complex over $(A,B)$ for some $B$.
	\end{itemize}
\end{ex}
\begin{ex}
	More concretely, let $A=(\begin{smallmatrix}k&k\\0 &k\end{smallmatrix})$ for some field $k$. This is not local since $A/J(A)\cong k\oplus k$.
	Furthermore, $\gldim A=1$. Now let $e_{11}$ and $e_{22}$ refer to the standard $2x2$ matrices with ones in the appropriate spots and zeros elsewhere.

	Then if $S_1=Ae_{11}$ and $S_2=\binom{0}{k}$, then we get a sequence 
	\[0\to S_1\to\binom{k}{k}\to S_2\to 0\]
	and so $\projdim S_1=0=\injdim S_2$ and $\projdim S_2=1=\injdim S_1$, giving us a counterexample when we don't have locality.
\end{ex}
\begin{ex}
	More simply, if $A=k[[t]]$, $\projdim A=0\ne1\projdim k.$
\end{ex}

\subsection{Some Review}
Let $X$ be a bounded (this can be defined more generally but James' definiton requires this) complex of left $A$-modules.
\begin{defn}
	The projective dimension is defined to be 
	\[\projdim X=\sup\{i|\Ext^i(X,M)\ne 0,\text{ some M}\in\Amod\}\]
	or equivalently
	\[\projdim X=\inf_P\sup\{i|P^{-i}\ne 0\}\]
	where $P$ ranges over all projective resolutions of $X$.
\end{defn}
\begin{defn}
	The injective dimension is defined to be 
	\[\injdim X=\sup\{i|\Ext^i(M,X)\ne 0,\text{ some M}\in\Amod\}\]
	or equivalently
	\[\injdim X=\inf_I\sup\{i|I^{-i}\ne 0\}\]
	where $I$ ranges over all injective resolutions of $X$.
\end{defn}

Now let $A$ be local and write ${_A}k=A/J(A)$.
\begin{defn}
	Let $X$ be a bounded complex of $A$ modules. Then the \textbf{depth of $X$} is
	\[\operatorname{depth}X=\inf\{i|\Ext^i(k,X)\ne 0\}\]
\end{defn}
\begin{rmk}
	Notice that, in general, $\depth X\le \injdim X$.
\end{rmk}
\begin{rmk}
	In commutative algebra, the more natural definition is in terms of lengths of regular sequences. This ends up being 
	equivalent but requires a little work.
\end{rmk}
\begin{defn}
	Let $X$ be a bounded complex. Then 
	\[\inf X=\inf\{i|H^i(X)\ne 0\}\]
	and 
	\[\sup X=\sup\{i|H^i(X)\ne 0\}\]
\end{defn}
\begin{rmk}
	So then $\depth X=\inf(R\Hom_A(k,X)).$
\end{rmk}
\begin{lem}
	Let $A$ be a Noetherian local algebra and let $X\in\Dneg_{fg}(\Amod)$. Let $P$ be a minimal free resolution of $X$.
	Then 
	\[\projdim X=\max\{i|P^{-i}\ne 0\}\]
\end{lem}
\begin{prf}
	We always have that $\projdim X$ is less than or equal to this by the definition. So it suffices to show the reverse inequality.
	That is, we want to show that $\projdim X\ge i$ if $P^{-i}\ne 0.$

	Since $P$ is minimal, the complex $\Hom_{\Ch(\Amod)}(P,k)$ has zero differential (since $\partial_P^i$ maps into $J(A)P^{i+1}$).
	But then computing:
	\[\Ext_A^i(X,k)=H^i(\Hom(P,k))=\Hom(P,k)^i=\Hom_A(P^{-i},k)\ne 0\]
	whence we can conclude that $\projdim X\ge i$.
\end{prf}

\subsection{Canonical Truncations}
\begin{defn}
	Let $X$ be a complex in $\Amod$. The \textbf{$n^{th}$ bounded above truncation of $X$ is}
	\[\calT^{\le n}X=\cdots\to X^i\to\cdots\to X^{n-1}\to\ker(\partial_X^n)\to 0\to \cdots\]
	and the \textbf{$n^{th}$ bounded below truncation} is
	\[\calT^{\ge n}X=\cdots 0\to\coker(\partial_X^{n-1})\to X^{n+1}\to X^{n+2}\to\cdots\]
\end{defn}
\begin{thm}
	Let $A$ be a Noetherian local algebra and let $X,Y\in\Db_{fg}(\Amod)$. Suppose $\projdim X<\infty$.
	Then 
	\[\sup(R\Hom_A(X,Y))=\projdim X+\sup Y.\]
\end{thm}
\begin{prf}
	Not enough time for the full thing. So we prove ``$\le$''. Let $P$ be a minimal free resolution of $X$. Then 
	$P=0\to P^{-d}\to\cdots\to P^b\to 0\to\cdots$. Then $d=\projdim X$.

	Say $Y=0\to Y^a\to\cdots\to Y^s\to 0$, so $\sup Y=s$. But notice $R\Hom(X,Y)=\Hom_{\Ch(\Amod)}(P,Y)$
	so for $i>d+s$,
	\[\Hom(P,Y)^i=\prod_{s\in\bbZ}\Hom_A(P^s,Y^{s+i})=0\]
	so therefore $\sup \Hom(P,Y)\le d+s$.
\end{prf}
\begin{cor}
	Let $Y$ be a finitely generated module and $X$ a module with finite projective dimension. Then 
	\[\projdim X=\sup(R\Hom_A(M,N)).\]
\end{cor}
